---
output: github_document
bibliography: references.bib
nocite: '@*'
vignette: >
  %\VignetteIndexEntry{README}
  %\VignetteEngine{knitr::rmarkdown}

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# twohundredfiftythings

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`{twohundredfiftythings}` is a tiny R package that allows the user to access Michael Sorkin's list of things an architect should know. The list was originally published in "What Goes Up: The Rights and Wrongs to a City" (@sorkin_what_2018). 

## Background  

I was inspired to make this package after listening to [99% Invisible's](https://99percentinvisible.org/) 400th episode: ["The Smell of Concrete After Rain"](https://99percentinvisible.org/episode/the-smell-of-concrete-after-rain/). Hearing Roman Mars read through a small selection of these things, I decided to read the entire list. I figured it would be nice to read one of these every once in a while, so I made this package to return a random "thing" from the list.  

I was also inspired by my dear friend Katie Jolly's R package, [`{advicegiveR}`](https://github.com/katiejolly/advicegiveR). Katie introduced me to 99pi, and I am forever grateful.  

## Installation

You can install the development version of `{twohundredfiftythings}` using `remotes::install_github()`

```{r, eval = FALSE}
remotes::install_github("eroten/twohundredfiftythings")
```

## Examples  

The only function is `what_should_an_architect_know()`. To get a random thing, leave the inputs empty.  


```{r, warning = FALSE, message = FALSE}
library(twohundredfiftythings)
library(dplyr)

set.seed(99)
what_should_an_architect_know()
```

You can also access a specific thing from the list. 

```{r}
what_should_an_architect_know(40)
```

Input a vector of integers to get multiple things from the list. 

```{r, warning = FALSE}
what_should_an_architect_know(thing = c(1, 80))
```

You can access the full list, as well. 

```{r}
head(things_an_architect_should_know)
```


## Code of Conduct

Please note that the twohundredfiftythings project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## References
